### 2022-12-05 Bike-share-spatial-equity/Bike-share-spatial-equity.Rmd
Initialized renv for greater reproducibility, updated README with bibliographical info and created a map for sharing to Mastodon

```{r install-data-package, include = FALSE}
# Run only once if needed to install data package `sobiEquity`
if (!require("sobiEquity", character.only = TRUE)) {
      devtools::install_github("https://github.com/paezha/Accessibility-Sobi-Hamilton", subdir = "sobiEquity")
  }
```

```{r load-packages, include=FALSE}
library(biscale)
library(cowplot)
library(data.table)
library(disk.frame)
library(dplyr)
library(gdistance)
library(ggmap)
library(ggspatial)
library(gridExtra)
library(kableExtra)
library(pycno)
library(r5r) # the r5r package requires Java Development Kit version 11, which can be downloaded from https://www.oracle.com/java/technologies/javase-jdk11-downloads.htmllibrary(readr)
library(raster)
library(rgdal)
library(sf)
library(sobiEquity) # Data package
library(tidyverse)
library(tinytex)
library(units)
```

@@

>>>>

```{r load-packages-1, include=FALSE}
library(glue)
library(here)
```

```{r install-data-package, include = FALSE, renv.ignore=TRUE}
# Run only once if needed to install data package `sobiEquity`
if (!require("sobiEquity", character.only = TRUE)) {
      install.packages(glue(here::here(),'/sobiEquity_0.1.0.tar.gz'), repos=NULL, type='source')
  }
```

```{r load-packages-2, include=FALSE}
library(biscale)
library(cowplot)
library(data.table)
#library(disk.frame)
library(dplyr)
library(gdistance)
library(ggmap)
library(ggplot2)
library(ggspatial)
library(glue)
library(gridExtra)
library(here)
library(kableExtra)
library(pycno)
#library(r5r) # the r5r package requires Java Development Kit version 11, which can be downloaded from https://www.oracle.com/java/technologies/javase-jdk11-downloads.htmllibrary(readr)
library(raster)
#library(rgdal)
library(sf)
library(sobiEquity) # Data package
library(tidyr)
#library(tinytex)
library(units)
```

@@

<!--

MAPSTODON MONDAY DEC. 5, 2022

```{r figure-8-a, include=FALSE}
#accessibility plot for current system with equity stations at 10 minutes walk
accessibility_10min <- accessibility %>% 
  dplyr::filter(threshold == "10 min",
                system == "All stations")  %>%
  mutate(system = "With equity stations",
         accessibility = accessibility * 1000, # Convert to racks per 1,000 person
         accessibility = cut(accessibility,
                             breaks = c(-Inf, 0.04, 0.3, 2.00, Inf), 
                             labels = c("<0.04", "0.04-0.3", "0.3-2.00", ">2.00")),
         accessibility = factor(accessibility,
                                levels = c( ">2.00", "0.3-2.00", "0.04-0.3", "<0.04"),
                                ordered = TRUE))

acc_10_all <- ggplot() +
  geom_sf(data = population_50x50,
          color = "lightgray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_10min), 
                         st_coordinates(accessibility_10min)),
            aes(x = X, 
                y = Y, 
                fill = accessibility)) +
  scale_fill_viridis_d(name = "Accessibility\n(racks/1,000 person)",
                    option = "viridis",
                    direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ .)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_north_arrow(location = "tr", which_north = "true", 
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_fancy_orienteering)

```{r figure-8-b, include=FALSE}
#accessibility plot for current system without equity stations at 10 minutes walk
accessibility_10min <- accessibility %>% 
  dplyr::filter(threshold == "10 min",
                system == "Conventional")  %>%
  mutate(system = "Without equity stations",
         accessibility = accessibility * 1000, # Convert to racks per 1,000 person
         accessibility = cut(accessibility,
                             breaks = c(-Inf, 0.04, 0.3, 2.00, Inf), 
                             labels = c("<0.04", "0.04-0.3", "0.3-2.00", ">2.00")),
         accessibility = factor(accessibility,
                                levels = c( ">2.00", "0.3-2.00", "0.04-0.3", "<0.04"),
                                ordered = TRUE))

acc_10_conv <- ggplot() +
  geom_sf(data = population_50x50,
          color = "lightgray") +
  geom_tile(data = cbind(st_drop_geometry(accessibility_10min), 
                         st_coordinates(accessibility_10min)),
            aes(x = X, 
                y = Y, 
                fill = accessibility)) +
  scale_fill_viridis_d(name = "Accessibility\n(racks/1,000 person)",
                    option = "viridis",
                    direction = 1) +
  geom_sf(data = sobi_service,
          fill = NA) +
  facet_grid(system ~ .)  +
  geom_sf(data = community_downtown %>%
            dplyr::filter(NAME == "Hamilton"),
          fill = NA,
          color = "dark green") +
  theme(panel.background = element_rect(fill = "white"),
        axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())  +
  annotation_scale(location = "bl", width_hint = 0.4,
                   pad_x = unit(0.4, "in"), pad_y = unit(0.2, "in"))
```

```{r figure-8, echo=FALSE, fig.align = 'center', out.width = "90%", fig.cap = "Accessibility at 10 minutes walk (maximum threshold) compared between current system with equity stations and the original system without equity stations."}
ggdraw() + 
  draw_plot(acc_10_conv + 
              theme(legend.position = "none"), 
            0.00, 0.5, 1, 0.5) + 
  draw_plot(acc_10_all + 
              theme(legend.position = "none"), 0.00, 0.0, 1, 0.5) + 
  draw_plot(acc_10_legend, 0.01, 0.4, 0.2, 0.2)

ggsave("acc_10_mapstodon.jpeg",
       width = 8,
       height = 7)
```

-->

### 2022-12-05 README.Rmd
Initialized renv for greater reproducibility, updated README with bibliographical info and created a map for sharing to Mastodon

Forthcoming in *Transportation Research Part D: Transport and Environment*

@@

```{r echo=FALSE}
rm(list = ls())
```

```{r install-data-package, include = FALSE}
# Run only once if needed to install data package `sobiEquity`
if (!require("sobiEquity", character.only = TRUE)) {
      devtools::install_github("https://github.com/paezha/Accessibility-Sobi-Hamilton", subdir = "sobiEquity")
  }
```

```{r load-packages, include=FALSE}
library(biscale)
library(cowplot)
library(data.table)
library(disk.frame)
library(dplyr)
library(gdistance)
library(ggmap)
library(ggspatial)
library(gridExtra)
library(kableExtra)
library(pycno)
library(r5r) # the r5r package requires Java Development Kit version 11, which can be downloaded from https://www.oracle.com/java/technologies/javase-jdk11-downloads.htmllibrary(readr)
library(raster)
library(rgdal)
library(sf)
library(sobiEquity) # Data package
library(tidyverse)
library(tinytex)
library(units)
```

>>>>

Desjardins, E., Higgins, C.D., Paez, A. (2022) Examining spatial equity of bike share: A balanced floating catchment area approach, Transportation Research Part D (102) 103091 (doi.org/10.1016/j.trd.2021.103091)

@@

```{r load-packages-1, include=FALSE}
library(glue)
library(here)
```

```{r install-data-package, include = FALSE, renv.ignore=TRUE}
# Run only once if needed to install data package `sobiEquity`
if (!require("sobiEquity", character.only = TRUE)) {
      install.packages(glue(here::here(),'/sobiEquity_0.1.0.tar.gz'), repos=NULL, type='source')
  }
```

```{r load-packages-2, include=FALSE}
library(biscale)
library(cowplot)
library(data.table)
#library(disk.frame)
library(dplyr)
library(gdistance)
library(ggmap)
library(ggplot2)
library(ggspatial)
library(glue)
library(gridExtra)
library(here)
library(kableExtra)
library(pycno)
#library(r5r) # the r5r package requires Java Development Kit version 11, which can be downloaded from https://www.oracle.com/java/technologies/javase-jdk11-downloads.htmllibrary(readr)
library(raster)
#library(rgdal)
library(sf)
library(sobiEquity) # Data package
library(tidyr)
#library(tinytex)
library(units)
```
